### 2022-08-22 Bloods Data Sheet.Rmd
Imported Data

#Main Data Sheet
```{r}
main_df <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2021\\Study 2 and 3\\AAADATA\\Bloods Data\\MAIN_DATA_SHEET.csv")
```

#Calculating Dilution Factor
```{r}
main_df <- main_df%>%
  filter(!Sample %in% 22)%>%
  filter(!Sample %in% 235)%>%
  filter(!Sample %in% 236)%>%
  mutate(Dilution_Factor = ((Sample.Volume+Solution)/Sample.Volume))%>%
  mutate(cal_LDH = LDH*Dilution_Factor)%>%
  mutate(cal_CK = CK*Dilution_Factor)%>%
  mutate(cal_Na = Na*Dilution_Factor)%>%
  mutate(cal_K = K*Dilution_Factor)%>%
  mutate(cal_Cl = Cl*Dilution_Factor)%>%
  drop_na(Sample)

```

```{r}
histogram(main_df$cal_Na)
```

#Summary Data
```{r}
BlaSUM <- main_df%>%
summarySE(measurevar = "Bla", groupvar =c("Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

LDHSUM <- main_df%>%
summarySE(measurevar = "cal_LDH", groupvar =c("Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

CKSUM <- main_df%>%
summarySE(measurevar = "cal_CK", groupvar =c("Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

NaSUM <- main_df%>%
summarySE(measurevar = "cal_Na", groupvar =c("Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

KSUM <- main_df%>%
summarySE(measurevar = "cal_K", groupvar =c("Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

ClSUM <- main_df%>%
summarySE(measurevar = "cal_Cl", groupvar =c("Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

### 2022-08-22 Bloods Data Sheet.Rmd
Added draft plots

@@
   mutate(cal_CK = CK*Dilution_Factor)%>%
-  mutate(cal_Na = Na*Dilution_Factor)%>%
-  mutate(cal_K = K*Dilution_Factor)%>%
-  mutate(cal_Cl = Cl*Dilution_Factor)%>%
+  mutate(cal_Na = (Na-0.68)*Dilution_Factor)%>%
+  mutate(cal_K = (K-0.025)*Dilution_Factor)%>%
+  mutate(cal_Cl = (Cl-2.8)*Dilution_Factor)%>%
   drop_na(Sample)
+main_df$Time_Point <- as.factor(main_df$Time_Point)
 

### 2022-08-22 Draft Plots.Rmd
Added draft plots

#Draft Plots
##Blood Lactate
```{r}
Bla_SUM<-main_df%>%
  summarySE(measurevar = "Bla", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
Bla_SUM$Session_f = factor(Bla_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

Bla_SUM$Speed_f = factor(Bla_SUM$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

Bla_SUM$Time_Point_f = factor(Bla_SUM$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

Bla_PLOT_1 <- ggplot(Bla_SUM, aes(x = Time_Point_f, y= Bla))+
            geom_errorbar(aes(ymin = Bla-se, ymax =Bla+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_colour_manual(name = "Session_f",
                            labels = Session_f.labs,
                            values = c("black", "black", "black", "black"))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Blood Lactate Concentration (mmol/L) \n",breaks = c(0,1,2,3,4,5,6), limits = c(0,6))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))

Bla_PLOT_1

```

## Lactate Dehydrogenase
```{r}
LDH_SUM<-main_df%>%
  summarySE(measurevar = "cal_LDH", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
LDH_SUM$Session_f = factor(LDH_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

LDH_SUM$Speed_f = factor(LDH_SUM$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

LDH_SUM$Time_Point_f = factor(LDH_SUM$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

LDH_PLOT_1 <- ggplot(LDH_SUM, aes(x = Time_Point_f, y= cal_LDH))+
            geom_errorbar(aes(ymin = cal_LDH-se, ymax =cal_LDH+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_colour_manual(name = "Session_f",
                            labels = Session_f.labs,
                            values = c("black", "black", "black", "black"))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Lactate Dehydrogenase (units/L) \n",breaks = c(150,160,170,180,190,200,210,220,230,240,250,260,270), limits = c(150,270))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))

LDH_PLOT_1

```

##Creatine Kinase
```{r}
CK_SUM<-main_df%>%
  summarySE(measurevar = "cal_CK", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
CK_SUM$Session_f = factor(CK_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

CK_SUM$Speed_f = factor(CK_SUM$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

CK_SUM$Time_Point_f = factor(CK_SUM$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

CK_PLOT_1 <- ggplot(CK_SUM, aes(x = Time_Point_f, y= cal_CK))+
            geom_errorbar(aes(ymin = cal_CK-se, ymax =cal_CK+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_colour_manual(name = "Session_f",
                            labels = Session_f.labs,
                            values = c("black", "black", "black", "black"))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Creatine Kinase (units/L) \n",breaks = c(125,150,175,200,225,250,275,300,325,350), limits = c(125,350))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))

CK_PLOT_1

```

##Sodium
```{r}
Na_SUM<-main_df%>%
  summarySE(measurevar = "cal_Na", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
Na_SUM$Session_f = factor(Na_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

Na_SUM$Speed_f = factor(Na_SUM$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

Na_SUM$Time_Point_f = factor(Na_SUM$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

Na_PLOT_1 <- ggplot(Na_SUM, aes(x = Time_Point_f, y= cal_Na))+
            geom_errorbar(aes(ymin = cal_Na-se, ymax =cal_Na+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_colour_manual(name = "Session_f",
                            labels = Session_f.labs,
                            values = c("black", "black", "black", "black"))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Sodium \n",breaks = c(125,150,175,200), limits = c(125,200))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))

Na_PLOT_1

```

##Potassium
```{r}
K_SUM<-main_df%>%
  summarySE(measurevar = "cal_K", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
K_SUM$Session_f = factor(K_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

K_SUM$Speed_f = factor(K_SUM$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

K_SUM$Time_Point_f = factor(K_SUM$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

K_PLOT_1 <- ggplot(K_SUM, aes(x = Time_Point_f, y= cal_K))+
            geom_errorbar(aes(ymin = cal_K-se, ymax =cal_K+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_colour_manual(name = "Session_f",
                            labels = Session_f.labs,
                            values = c("black", "black", "black", "black"))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Potassium \n",breaks = c(4,5,6,7,8,9,10), limits = c(4,10))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))

K_PLOT_1

```

##Chlorine
```{r}
Cl_SUM<-main_df%>%
  summarySE(measurevar = "cal_Cl", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
```

```{r}
Cl_SUM$Session_f = factor(Cl_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

Cl_SUM$Speed_f = factor(Cl_SUM$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

Cl_SUM$Time_Point_f = factor(Cl_SUM$Time_Point, levels=c("1", "2", "3"))
Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("1", "2", "3")

Cl_PLOT_1 <- ggplot(Cl_SUM, aes(x = Time_Point_f, y= cal_Cl))+
            geom_errorbar(aes(ymin = cal_Cl-se, ymax =cal_Cl+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_colour_manual(name = "Session_f",
                            labels = Session_f.labs,
                            values = c("black", "black", "black", "black"))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            #scale_y_continuous(name = "Chlorine \n",breaks = c(4,5,6,7,8,9,10), limits = c(4,10))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))

Cl_PLOT_1

```

### 2022-08-22 Bloods Data Sheet.Rmd
Export Data Sheet

@@
 
+```
+
+```{r}
+write.csv(main_df,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Main_Data_Frame (22-08-2022).csv",row.names = FALSE)
 ```
@@
 ```
+
+```{r}
+main_df_PRE <- main_df%>%
+  filter(!Time_Point %in% "2")%>%
+  filter(!Time_Point %in% "3")
+
+main_df <- main_df[main_df$cal_Cl <300,]
+TRUNK_MAX_X <- TRUNK_MAX_X[TRUNK_MAX_X$TrunkAngle_X <10,]
+```

### 2022-08-22 Draft Plots.Rmd
Export Data Sheet

@@
             xlab("\n Collection Time Point")+
-            #scale_y_continuous(name = "Chlorine \n",breaks = c(4,5,6,7,8,9,10), limits = c(4,10))+
+            scale_y_continuous(name = "Chlorine \n",breaks = c(90,100,110,120), limits = c(90,120))+
             scale_x_discrete(breaks=c("1", "2", "3"),

### 2022-08-23 Bloods Data Sheet.Rmd
data editing

--- 2022-08-22 Bloods Data Sheet.Rmd
@@
 main_df <- main_df%>%
-  filter(!Sample %in% 22)%>%
+  #filter(!Sample %in% 22)%>%
   filter(!Sample %in% 235)%>%
@@
   mutate(cal_CK = CK*Dilution_Factor)%>%
-  mutate(cal_Na = Na*Dilution_Factor)%>%
-  mutate(cal_K = K*Dilution_Factor)%>%
-  mutate(cal_Cl = Cl*Dilution_Factor)%>%
+  mutate(cal_Na = (Na-0.68)*Dilution_Factor)%>%
+  mutate(cal_K = (K-0.025)*Dilution_Factor)%>%
+  mutate(cal_Cl = (Cl-2.8)*Dilution_Factor)%>%
   drop_na(Sample)
+main_df$Time_Point <- as.factor(main_df$Time_Point)
 
+```
+
+```{r}
+write.csv(main_df,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Main_Data_Frame (23-08-2022).csv",row.names = FALSE)
 ```

### 2022-08-25 Bloods Data Sheet.Rmd
Extracted draft plots

@@
 ```{r}
-write.csv(main_df,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Main_Data_Frame (23-08-2022).csv",row.names = FALSE)
+write.csv(main_df,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Main_Data_Frame (25-08-2022).csv",row.names = FALSE)
 ```

### 2022-08-25 Draft Plots.Rmd
Extracted draft plots

@@
 Bla_PLOT_1
+
+```
+
+```{r}
+ggsave(plot=Bla_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Blaplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
 
@@
 
+```{r}
+ggsave(plot=LDH_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//LDHplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
 ##Creatine Kinase
@@
 CK_PLOT_1
+
+```
+
+```{r}
+ggsave(plot=CK_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//CKplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
 
@@
 
+```{r}
+ggsave(plot=Na_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//NAplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
 ##Potassium
@@
 K_PLOT_1
+
+```
+
+```{r}
+ggsave(plot=K_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Kplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
 
@@
 ```
+
+```{r}
+ggsave(plot=Cl_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Clplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```

### 2022-08-26 Bloods Data Sheet.Rmd
added cleaned data sheet and plots

@@
 main_df <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2021\\Study 2 and 3\\AAADATA\\Bloods Data\\MAIN_DATA_SHEET.csv")
+```
+
+```{r}
+main_df2 <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Main_Data_Frame (Outliers_Removed).csv")
 ```
@@
 
+```
+
+```{r}
+main_df2 <- main_df2%>%
+  #filter(!Sample %in% 22)%>%
+  filter(!Sample %in% 235)%>%
+  filter(!Sample %in% 236)%>%
+  mutate(Dilution_Factor = ((Sample.Volume+Solution)/Sample.Volume))%>%
+  mutate(cal_LDH = LDH*Dilution_Factor)%>%
+  mutate(cal_CK = CK*Dilution_Factor)%>%
+  mutate(cal_Na = (Na-0.68)*Dilution_Factor)%>%
+  mutate(cal_K = (K-0.025)*Dilution_Factor)%>%
+  mutate(cal_Cl = (Cl-2.8)*Dilution_Factor)%>%
+  drop_na(Sample)
+main_df2$Time_Point <- as.factor(main_df2$Time_Point)
+
+```
+
+```{r}
+boxplot(cal_Cl ~ Session + Time_Point, data = main_df2)
 ```

### 2022-08-26 Draft Plots.Rmd
added cleaned data sheet and plots

@@
 
+### Lactate Dehydrogenase PLot 2
+```{r}
+LDH_SUM2<-main_df2%>%
+  summarySE(measurevar = "cal_LDH", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+```
+
+```{r}
+LDH_SUM2$Session_f = factor(LDH_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+LDH_SUM2$Speed_f = factor(LDH_SUM2$Speed, levels=c("SW", "FW"))
+ Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ names(Speed.labs)<-c("SW", "FW")
+
+LDH_SUM2$Time_Point_f = factor(LDH_SUM2$Time_Point, levels=c("1", "2", "3"))
+Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("1", "2", "3")
+
+LDH_PLOT_2 <- ggplot(LDH_SUM2, aes(x = Time_Point_f, y= cal_LDH))+
+            geom_errorbar(aes(ymin = cal_LDH-se, ymax =cal_LDH+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(22, 15, 21, 16))+
+            theme_classic()+
+            theme(legend.position="right", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Lactate Dehydrogenase (units/L) \n",breaks = c(150,160,170,180,190,200,210,220,230,240,250,260,270), limits = c(150,270))+
+            scale_x_discrete(breaks=c("1", "2", "3"),
+              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
+
+LDH_PLOT_2
+
+```
+```{r}
+LDH_Grouping <- ggarrange(LDH_PLOT_1,LDH_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")
+
+LDH_Grouping
+```
+
+```{r}
+ggsave(plot=LDH_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//LDHgrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
 ##Creatine Kinase
@@
 ggsave(plot=CK_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//CKplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
+###CK_PLOT2
+```{r}
+CK_SUM2<-main_df2%>%
+  summarySE(measurevar = "cal_CK", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+```
+
+```{r}
+CK_SUM2$Session_f = factor(CK_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+CK_SUM2$Speed_f = factor(CK_SUM2$Speed, levels=c("SW", "FW"))
+ Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ names(Speed.labs)<-c("SW", "FW")
+
+CK_SUM2$Time_Point_f = factor(CK_SUM2$Time_Point, levels=c("1", "2", "3"))
+Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("1", "2", "3")
+
+CK_PLOT_2 <- ggplot(CK_SUM2, aes(x = Time_Point_f, y= cal_CK))+
+            geom_errorbar(aes(ymin = cal_CK-se, ymax =cal_CK+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(22, 15, 21, 16))+
+            theme_classic()+
+            theme(legend.position="right", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Creatine Kinase (units/L) \n",breaks = c(100,125,150,175,200,225,250,275,300,325,350), limits = c(100,350))+
+            scale_x_discrete(breaks=c("1", "2", "3"),
+              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
+
+CK_PLOT_2
+
+```
+
+```{r}
+ggsave(plot=CK_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//CKplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
+```{r}
+CK_Grouping <- ggarrange(CK_PLOT_1,CK_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")
+
+CK_Grouping
+```
+```{r}
+ggsave(plot=CK_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//CKgrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
 
@@
 
+###Sodum PLot 2
+```{r}
+Na_SUM2<-main_df2%>%
+  summarySE(measurevar = "cal_Na", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+```
+
+```{r}
+Na_SUM2$Session_f = factor(Na_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+Na_SUM2$Speed_f = factor(Na_SUM2$Speed, levels=c("SW", "FW"))
+ Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ names(Speed.labs)<-c("SW", "FW")
+
+Na_SUM2$Time_Point_f = factor(Na_SUM2$Time_Point, levels=c("1", "2", "3"))
+Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("1", "2", "3")
+
+Na_PLOT_2 <- ggplot(Na_SUM2, aes(x = Time_Point_f, y= cal_Na))+
+            geom_errorbar(aes(ymin = cal_Na-se, ymax =cal_Na+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(22, 15, 21, 16))+
+            theme_classic()+
+            theme(legend.position="right", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Sodium \n",breaks = c(125,150,175,200), limits = c(125,200))+
+            scale_x_discrete(breaks=c("1", "2", "3"),
+              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
+
+Na_PLOT_2
+
+```
+
+```{r}
+ggsave(plot=Na_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//NAplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
+```{r}
+NA_Grouping <- ggarrange(Na_PLOT_1,Na_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")
+
+NA_Grouping
+```
+
+```{r}
+ggsave(plot=NA_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Nagrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
 ##Potassium
@@
 ggsave(plot=K_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Kplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
+###Potassium Plot 2
+```{r}
+K_SUM2<-main_df2%>%
+  summarySE(measurevar = "cal_K", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+```
+
+```{r}
+K_SUM2$Session_f = factor(K_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+K_SUM2$Speed_f = factor(K_SUM2$Speed, levels=c("SW", "FW"))
+ Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ names(Speed.labs)<-c("SW", "FW")
+
+K_SUM2$Time_Point_f = factor(K_SUM2$Time_Point, levels=c("1", "2", "3"))
+Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("1", "2", "3")
+
+K_PLOT_2 <- ggplot(K_SUM2, aes(x = Time_Point_f, y= cal_K))+
+            geom_errorbar(aes(ymin = cal_K-se, ymax =cal_K+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(22, 15, 21, 16))+
+            theme_classic()+
+            theme(legend.position="right", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Potassium \n",breaks = c(4,5,6,7,8,9,10), limits = c(4,10))+
+            scale_x_discrete(breaks=c("1", "2", "3"),
+              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
+
+K_PLOT_2
+
+```
+
+```{r}
+ggsave(plot=K_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Kplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
+```{r}
+K_Grouping <- ggarrange(K_PLOT_1,K_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")
+
+K_Grouping
+```
+
+```{r}
+ggsave(plot=K_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Kgrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
 
@@
 ```
+
+###Chorine PLot 2
+```{r}
+Cl_SUM2<-main_df2%>%
+  summarySE(measurevar = "cal_Cl", groupvar =c("Session","Time_Point", "Speed","BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+```
+
+```{r}
+Cl_SUM2$Session_f = factor(Cl_SUM2$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+Cl_SUM2$Speed_f = factor(Cl_SUM2$Speed, levels=c("SW", "FW"))
+ Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ names(Speed.labs)<-c("SW", "FW")
+
+Cl_SUM2$Time_Point_f = factor(Cl_SUM2$Time_Point, levels=c("1", "2", "3"))
+Time_Point.labs<- c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("1", "2", "3")
+
+Cl_PLOT_2 <- ggplot(Cl_SUM2, aes(x = Time_Point_f, y= cal_Cl))+
+            geom_errorbar(aes(ymin = cal_Cl-se, ymax =cal_Cl+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(22, 15, 21, 16))+
+            theme_classic()+
+            theme(legend.position="right", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Chlorine \n",breaks = c(90,100,110,120), limits = c(90,120))+
+            scale_x_discrete(breaks=c("1", "2", "3"),
+              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
+
+Cl_PLOT_2
+
+```
+
+```{r}
+ggsave(plot=Cl_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Clplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
+```{r}
+Cl_Grouping <- ggarrange(Cl_PLOT_1,Cl_PLOT_2,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")
+
+Cl_Grouping
+```
+
+```{r}
+ggsave(plot=Cl_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Clgrouping_Draft(26-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```

### 2022-08-31 Bloods Data Sheet.Rmd
created plots for presentation

@@
 ```
+
+#calculating Percentage Change
+##CK
+```{r}
+CK_PCHANGE <- main_df2%>%
+  summarySE(measurevar = "cal_CK", groupvar =c("Session", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```
+
+```{r}
+write.csv(CK_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\CK_PCHANGE (29-08-2022).csv",row.names = FALSE)
+```
+
+```{r}
+CK_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\CK_PCHANGE (29-08-2022).csv")
+```
+
+```{r}
+CK_PCHANGE_CL<-CK_PCHANGE_CL%>%
+  mutate(P_CHANGE = ((CK_POST-CK_PRE)/CK_PRE)*100)
+
+CK_PCHANGET2_SUM <-CK_PCHANGE_CL%>% 
+summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "Speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```
+
+```{r}
+names(main_df2)
+```
+
+##LDH
+```{r}
+LDH_PCHANGE <- main_df2%>%
+  summarySE(measurevar = "cal_LDH", groupvar =c("Session", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```
+
+```{r}
+write.csv(LDH_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\LDH_PCHANGE (29-08-2022).csv",row.names = FALSE)
+
+LDH_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\LDH_PCHANGE (29-08-2022).csv")
+```
+
+```{r}
+LDH_PCHANGE_CL<-LDH_PCHANGE_CL%>%
+  mutate(P_CHANGE = ((LDH_POST-LDH_PRE)/LDH_PRE)*100)
+
+LDH_PCHANGET2_SUM <-LDH_PCHANGE_CL%>% 
+summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "Speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```

### 2022-08-31 Bloods_LMM.Rmd
created plots for presentation

#Blood Lactate
```{r}
BlaLMM <- lmer(Bla ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
summary(BlaLMM)
pairwise_Bla <- emmeans(BlaLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwise_Bla
```

```{r}
tab_model(BlaLMM)
```

#Creatine Kinase
```{r}
CKLMM <- lmer(P_CHANGE ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = CK_PCHANGE_CL)
summary(CKLMM)
pairwiseCK <- emmeans(CKLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwiseCK
```
```{r}
tab_model(CKLMM)
```

#Lactate Dehydrogenase
```{r}
LDHLMM <- lmer(P_CHANGE ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = LDH_PCHANGE_CL)
summary(LDHLMM)
pairwiseLDH <- emmeans(LDHLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
pairwiseLDH
```

```{r}
tab_model(LDHLMM)
```

```{r}
names(LDH_PCHANGE_CL)
```

### 2022-08-31 Draft Plots.Rmd
created plots for presentation

@@
 
-Bla_SUM$Speed_f = factor(Bla_SUM$Speed, levels=c("SW", "FW"))
+Bla_SUM$Speed_f = factor(Bla_SUM$Speed, levels=c("SLOW", "FAST"))
  Speed.labs<- c("Low-Intensity","Moderate-Intensity")
- names(Speed.labs)<-c("SW", "FW")
+ names(Speed.labs)<-c("SLOW", "FAST")
 
@@
 
+FWBFR_Bla_Finger <- data.frame(Time_Point_f = c("2"),
+                         Bla = c(6),
+                         Session_f = c("FWBFR"))
+
+FWBFR_Bla_Toe <- data.frame(Time_Point_f = c("3"),
+                         Bla = c(6),
+                         Session_f = c("FWBFR"))
+
+FW_Bla_Toe <- data.frame(Time_Point_f = c("3"),
+                         Bla = c(5),
+                         Session_f = c("FW"))
+
+SWBFR_Bla_Finger <- data.frame(Time_Point_f = c("2"),
+                         Bla = c(4),
+                         Session_f = c("SWBFR"))
+
+SWBFR_Bla_Toe <- data.frame(Time_Point_f = c("3"),
+                         Bla = c(4),
+                         Session_f = c("SWBFR"))
+
 Bla_PLOT_1 <- ggplot(Bla_SUM, aes(x = Time_Point_f, y= Bla))+
-            geom_errorbar(aes(ymin = Bla-se, ymax =Bla+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
-            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+            geom_errorbar(aes(ymin = Bla-se, ymax =Bla+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
 
@@
                            labels = Session_f.labs,
-                           values = c(22, 15, 21, 16))+
+                           values = c(21, 16,22, 15))+
             theme_classic()+
-            theme(legend.position="right", legend.title=element_blank())+
+            theme(legend.position="bottom", legend.title=element_blank())+
             xlab("\n Collection Time Point")+
@@
             scale_x_discrete(breaks=c("1", "2", "3"),
-              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
+              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))+
+
+                  theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
+                  axis.text.x=element_text(size=16, colour="black"),
+                  axis.text.y=element_text(size=16, colour="black"))+
+                  theme(axis.text.x=element_text(size=16, angle = 0),
+                   axis.title.x=element_text(size=16),
+                   axis.title.y=element_text(size=18),
+                   strip.text.y=element_text(size=14,face="italic"),
+                   strip.text.x=element_text(size=16,face="italic"),
+                   legend.title = element_blank())+
+                   theme(legend.text=element_text(size=16))+
+
+                  geom_text(size=6,data = FWBFR_Bla_Finger, label = "a #       ")+  
+                   geom_text(size=6,data = FWBFR_Bla_Toe, label = "a  #     ")+
+                   geom_text(size=6,data = FW_Bla_Toe, label = "a")+
+                   geom_text(size=6,data = SWBFR_Bla_Finger, label = "#")+
+                   geom_text(size=6,data = SWBFR_Bla_Toe, label = "#")
 
@@
 ```{r}
-ggsave(plot=Bla_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Blaplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+ggsave(plot=Bla_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Blaplot_Draft(31-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
 
@@
 Na_PLOT_2 <- ggplot(Na_SUM2, aes(x = Time_Point_f, y= cal_Na))+
-            geom_errorbar(aes(ymin = cal_Na-se, ymax =cal_Na+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
-            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+            geom_errorbar(aes(ymin = cal_Na-se, ymax =cal_Na+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
 
@@
                            labels = Session_f.labs,
-                           values = c(22, 15, 21, 16))+
+                           values = c(21, 16, 22, 15))+
             theme_classic()+
-            theme(legend.position="right", legend.title=element_blank())+
+            theme(legend.position="", legend.title=element_blank())+
             xlab("\n Collection Time Point")+
-            scale_y_continuous(name = "Sodium \n",breaks = c(125,150,175,200), limits = c(125,200))+
+            scale_y_continuous(name = "Sodium (mmol/L) \n",breaks = c(100,125,150,175,200), limits = c(100,200))+
             scale_x_discrete(breaks=c("1", "2", "3"),
-              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
+              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))+
+
+  theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
+                  axis.text.x=element_text(size=16, colour="black"),
+                  axis.text.y=element_text(size=16, colour="black"))+
+                  theme(axis.text.x=element_text(size=10, angle = 0),
+                   axis.title.x=element_text(size=16),
+                   axis.title.y=element_text(size=18),
+                   strip.text.y=element_text(size=14,face="italic"),
+                   strip.text.x=element_text(size=16,face="italic"),
+                   legend.title = element_blank())+
+                   theme(legend.text=element_text(size=16))
 
@@
 K_PLOT_2 <- ggplot(K_SUM2, aes(x = Time_Point_f, y= cal_K))+
-            geom_errorbar(aes(ymin = cal_K-se, ymax =cal_K+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
-            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+            geom_errorbar(aes(ymin = cal_K-se, ymax =cal_K+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
 
@@
                            labels = Session_f.labs,
-                           values = c(22, 15, 21, 16))+
+                           values = c(21, 16, 22, 15))+
             theme_classic()+
-            theme(legend.position="right", legend.title=element_blank())+
+            theme(legend.position="", legend.title=element_blank())+
             xlab("\n Collection Time Point")+
-            scale_y_continuous(name = "Potassium \n",breaks = c(4,5,6,7,8,9,10), limits = c(4,10))+
+            scale_y_continuous(name = "Potassium (mmol/L) \n",breaks = c(4,5,6,7,8,9,10), limits = c(4,10))+
             scale_x_discrete(breaks=c("1", "2", "3"),
-              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
+              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))+
+
+  theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
+                  axis.text.x=element_text(size=16, colour="black"),
+                  axis.text.y=element_text(size=16, colour="black"))+
+                  theme(axis.text.x=element_text(size=10, angle = 0),
+                   axis.title.x=element_text(size=16),
+                   axis.title.y=element_text(size=18),
+                   strip.text.y=element_text(size=14,face="italic"),
+                   strip.text.x=element_text(size=16,face="italic"),
+                   legend.title = element_blank())+
+                   theme(legend.text=element_text(size=16))
 
@@
 Cl_PLOT_2 <- ggplot(Cl_SUM2, aes(x = Time_Point_f, y= cal_Cl))+
-            geom_errorbar(aes(ymin = cal_Cl-se, ymax =cal_Cl+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
-            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+            geom_errorbar(aes(ymin = cal_Cl-se, ymax =cal_Cl+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
 
@@
                            labels = Session_f.labs,
-                           values = c(22, 15, 21, 16))+
+                           values = c(21, 16, 22, 15))+
             theme_classic()+
-            theme(legend.position="right", legend.title=element_blank())+
+            theme(legend.position="", legend.title=element_blank())+
             xlab("\n Collection Time Point")+
-            scale_y_continuous(name = "Chlorine \n",breaks = c(90,100,110,120), limits = c(90,120))+
+            scale_y_continuous(name = "Chlorine (mmol/L) \n",breaks = c(50,75,100,125,150), limits = c(50,150))+
             scale_x_discrete(breaks=c("1", "2", "3"),
-              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))
+              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))+
+  theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
+                  axis.text.x=element_text(size=16, colour="black"),
+                  axis.text.y=element_text(size=16, colour="black"))+
+                  theme(axis.text.x=element_text(size=10, angle = 0),
+                   axis.title.x=element_text(size=16),
+                   axis.title.y=element_text(size=18),
+                   strip.text.y=element_text(size=14,face="italic"),
+                   strip.text.x=element_text(size=16,face="italic"),
+                   legend.title = element_blank())+
+                   theme(legend.text=element_text(size=16))
 
@@
 ```
+
+#Percentage Change
+##CK
+CK_PCHANGET2_SUM
+
+```{r}
+CK_PCHANGET2_SUM$Session_f = factor(CK_PCHANGET2_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+#Cl_SUM2$Speed_f = factor(Cl_SUM2$Speed, levels=c("SW", "FW"))
+ #Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ #names(Speed.labs)<-c("SW", "FW")
+
+CK_PCHANGET2_SUM$Time_Point_f = factor(CK_PCHANGET2_SUM$Time_Point, levels=c("2", "3"))
+Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("2", "3")
+
+CK_PLOT_PCHANGE <- ggplot(CK_PCHANGET2_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
+            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(21, 16, 22, 15))+
+            theme_classic()+
+            ggtitle("Creatine Kinase")+
+            theme(plot.title = element_text(hjust = 0.5))+
+            theme(legend.position="", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Percentage Change \n",breaks = c(-10,0,10,20,30,40,50), limits = c(-10,50))+
+            scale_x_discrete(breaks=c("2", "3"),
+              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+
+
+             theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
+                  axis.text.x=element_text(size=16, colour="black"),
+                  axis.text.y=element_text(size=16, colour="black"))+
+                  theme(axis.text.x=element_text(size=16, angle = 0),
+                   axis.title.x=element_text(size=16),
+                   axis.title.y=element_text(size=18),
+                   strip.text.y=element_text(size=14,face="italic"),
+                   strip.text.x=element_text(size=16,face="italic"),
+                   legend.title = element_blank())+
+                   theme(legend.text=element_text(size=16))
+
+CK_PLOT_PCHANGE
+
+```
+##LDH
+```{r}
+LDH_PCHANGET2_SUM
+```
+
+```{r}
+LDH_PCHANGET2_SUM$Session_f = factor(LDH_PCHANGET2_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+#Cl_SUM2$Speed_f = factor(Cl_SUM2$Speed, levels=c("SW", "FW"))
+ #Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ #names(Speed.labs)<-c("SW", "FW")
+
+LDH_PCHANGET2_SUM$Time_Point_f = factor(LDH_PCHANGET2_SUM$Time_Point, levels=c("2", "3"))
+Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("2", "3")
+
+LDH_PLOT_PCHANGE <- ggplot(LDH_PCHANGET2_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
+            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(21, 16,22, 15))+
+            theme_classic()+
+            ggtitle("Lactate Dehydrogenase")+
+            theme(plot.title = element_text(hjust = 0.5))+
+            theme(legend.position="", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Percentage Change \n",breaks = c(-10,0,10,20,30,40,50), limits = c(-10,50))+
+            scale_x_discrete(breaks=c("2", "3"),
+              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+
+
+            theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
+                  axis.text.x=element_text(size=16, colour="black"),
+                  axis.text.y=element_text(size=16, colour="black"))+
+                  theme(axis.text.x=element_text(size=16, angle = 0),
+                   axis.title.x=element_text(size=16),
+                   axis.title.y=element_text(size=18),
+                   strip.text.y=element_text(size=14,face="italic"),
+                   strip.text.x=element_text(size=16,face="italic"),
+                   legend.title = element_blank())+
+                   theme(legend.text=element_text(size=16))
+
+LDH_PLOT_PCHANGE
+
+```
+
+```{r}
+PCHANGE_Grouping <- ggarrange(CK_PLOT_PCHANGE,LDH_PLOT_PCHANGE,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")
+
+PCHANGE_Grouping
+```
+
+```{r}
+ggsave(plot=PCHANGE_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//PCHANGE_Grouping_Draft(31-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
+
+```
+
+##Electrolyte Grouping
+```{r}
+ELECTROLYTE_Grouping <- ggarrange(Na_PLOT_2,Cl_PLOT_2,K_PLOT_2,labels=c("A", "B", "C"), ncol=3, nrow=1, common.legend = TRUE, legend = "bottom")
+
+ELECTROLYTE_Grouping
+```
+
+```{r}
+ggsave(plot=ELECTROLYTE_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//ELECTROLYTE_Grouping(31-08-2022).png", units = "in",width = 18, height = 8, dpi = 1200)
+
+```

### 2022-09-02 Bloods Data Sheet.Rmd
Dz export along with new LMM

@@
 ```{r}
-BlaSUM <- main_df%>%
-summarySE(measurevar = "Bla", groupvar =c("Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+BlaSUM <- main_df2%>%
+summarySE(measurevar = "Bla", groupvar =c("Session", "Speed", "BFR", "Time_Point", "Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
 
@@
 summarySE(measurevar = "cal_Cl", groupvar =c("Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+```
+
+```{r}
+write.csv(BlaSUM,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\BLA_sum (02-09-2022).csv",row.names = FALSE)
 ```

### 2022-09-02 Bloods_LMM.Rmd
Dz export along with new LMM

@@
 ```{r}
-names(LDH_PCHANGE_CL)
+names(main_df2)
+
 ```
+
+#Sodium
+```{r}
+NaLMM <- lmer(cal_Na ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
+summary(NaLMM)
+pairwise_NaLMM <- emmeans(NaLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
+pairwise_NaLMM
+```
+
+```{r}
+tab_model(NaLMM)
+```
+
+#Potassium
+```{r}
+KLMM <- lmer(cal_K ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
+summary(KLMM)
+pairwise_KLMM <- emmeans(KLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
+pairwise_KLMM
+```
+
+```{r}
+tab_model(KLMM)
+```
+
+#Chlorine
+
+```{r}
+ClLMM <- lmer(cal_Cl ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df2)
+summary(ClLMM)
+pairwise_ClLMM <- emmeans(ClLMM, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
+pairwise_ClLMM
+```
+
+```{r}
+tab_model(ClLMM)
+```

### 2022-09-05 Bloods_LMM.Rmd
tried different model

@@
 
-#Creatine Kinase
+#Creatine Kinase - Percentage Change
 ```{r}
@@
 tab_model(CKLMM)
+```
+
+#Creatine Kinase - Total Change
+```{r}
+#Cant use total change as the SWBFR is uncharacteristically low
+```
+
+```{r}
+main_df_noPRE<-main_df2%>%
+  filter(!Time_Point %in% "1")
+```
+
+```{r}
+CKLMM_Total <- lmer(cal_CK ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df_noPRE)
+summary(CKLMM_Total)
+pairwiseCK_total <- emmeans(CKLMM_Total, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
+pairwiseCK_total
+```
+```{r}
+tab_model(CKLMM_Total)
 ```

### 2022-09-12 Bloods Data Sheet.Rmd
Calculating percentage change for electrolytes

@@
 
-#calculating Percentage Change
+#Calculating Percentage Change
 ##CK
@@
 
-```{r}
-names(main_df2)
-```
-
 ##LDH
@@
 ```
+
+##Sodium
+```{r}
+sodium_PCHANGE <- main_df2%>%
+  summarySE(measurevar = "cal_Na", groupvar =c("Session", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```
+
+```{r}
+write.csv(sodium_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\sodium_PCHANGE (12-09-2022a).csv",row.names = FALSE)
+
+sodium_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\sodium_PCHANGE (12-09-2022).csv")
+```
+
+```{r}
+sodium_PCHANGE_CL<-sodium_PCHANGE_CL%>%
+  mutate(P_CHANGE = ((POST_EXERCISE-PRE_EXERCISE)/PRE_EXERCISE)*100)
+
+sodium_PCHANGE_CL_SUM <-sodium_PCHANGE_CL%>% 
+summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```
+
+##Potassium
+```{r}
+sodium_PCHANGE <- main_df2%>%
+  summarySE(measurevar = "cal_K", groupvar =c("Session", "Speed", "BFR", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```
+
+```{r}
+write.csv(sodium_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\potassium_PCHANGE (12-09-2022).csv",row.names = FALSE)
+
+potassium_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\potassium_PCHANGE (12-09-2022).csv")
+```
+
+```{r}
+potassium_PCHANGE_CL<-potassium_PCHANGE_CL%>%
+  mutate(P_CHANGE = ((POST_EXERCISE-PRE_EXERCISE)/PRE_EXERCISE)*100)
+
+potassium_PCHANGE_CL_SUM <-potassium_PCHANGE_CL%>% 
+summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "Speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```
+
+##Chloride
+```{r}
+chloride_PCHANGE <- main_df2%>%
+  summarySE(measurevar = "cal_Cl", groupvar =c("Session", "Speed", "BFR", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```
+
+```{r}
+write.csv(chloride_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\chloride_PCHANGE (12-09-2022).csv",row.names = FALSE)
+
+chloride_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\chloride_PCHANGE (12-09-2022).csv")
+```
+
+```{r}
+chloride_PCHANGE_CL<-chloride_PCHANGE_CL%>%
+  mutate(P_CHANGE = ((POST_EXERCISE-PRE_EXERCISE)/PRE_EXERCISE)*100)
+
+chloride_PCHANGE_CL_SUM <-chloride_PCHANGE_CL%>% 
+summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "Speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
+
+```

### 2022-09-12 Bloods_LMM.Rmd
Calculating percentage change for electrolytes

@@
 tab_model(CKLMM)
-```
-
-#Creatine Kinase - Total Change
-```{r}
-#Cant use total change as the SWBFR is uncharacteristically low
-```
-
-```{r}
-main_df_noPRE<-main_df2%>%
-  filter(!Time_Point %in% "1")
-```
-
-```{r}
-CKLMM_Total <- lmer(cal_CK ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = main_df_noPRE)
-summary(CKLMM_Total)
-pairwiseCK_total <- emmeans(CKLMM_Total, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
-pairwiseCK_total
-```
-```{r}
-tab_model(CKLMM_Total)
 ```

### 2022-09-12 Bloods_LMM.Rmd
Electrolytes Plots and LMM for Percentage Change

@@
 ```
-
-#Sodium
+#Total Change
+##Sodium
 ```{r}
@@
 
-#Potassium
+##Potassium
 ```{r}
@@
 
-#Chlorine
+##Chlorine
 
@@
 ```
+
+#Percentage Change
+##Sodium
+```{r}
+NaLMM_PCHANGE <- lmer(P_CHANGE ~ Time_Point + BFR + speed + Time_Point*BFR + Time_Point*speed + (1|Participant), data = sodium_PCHANGE_CL)
+summary(NaLMM_PCHANGE)
+pairwise_NaLMM_PCHANGE <- emmeans(NaLMM_PCHANGE, pairwise ~ Time_Point + BFR + speed + Time_Point*BFR + Time_Point*speed, adjust="holm")
+pairwise_NaLMM_PCHANGE
+```
+
+```{r}
+tab_model(NaLMM_PCHANGE)
+```
+
+##Potassium - Time points taken out currently
+```{r}
+KLMM_PCHANGE <- lmer(P_CHANGE ~ BFR + Speed + Speed*BFR + (1|Participant), data = potassium_PCHANGE_CL)
+summary(KLMM_PCHANGE)
+pairwise_KLMM_PCHANGE <- emmeans(KLMM_PCHANGE, pairwise ~ BFR + Speed + Speed*BFR, adjust="holm")
+pairwise_KLMM_PCHANGE
+```
+
+```{r}
+tab_model(KLMM_PCHANGE)
+```
+
+##Chloride
+```{r}
+ClLMM_PCHANGE <- lmer(P_CHANGE ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed + (1|Participant), data = chloride_PCHANGE_CL)
+summary(ClLMM_PCHANGE)
+pairwise_ClLMM_PCHANGE <- emmeans(ClLMM_PCHANGE, pairwise ~ Time_Point + BFR + Speed + Time_Point*BFR + Time_Point*Speed, adjust="holm")
+pairwise_ClLMM_PCHANGE
+```
+
+```{r}
+tab_model(ClLMM_PCHANGE)
+```

### 2022-09-12 Draft Plots.Rmd
Electrolytes Plots and LMM for Percentage Change

@@
 
+##Sodium
+```{r}
+sodium_PCHANGE_CL_SUM$Session_f = factor(sodium_PCHANGE_CL_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+#Cl_SUM2$Speed_f = factor(Cl_SUM2$Speed, levels=c("SW", "FW"))
+ #Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ #names(Speed.labs)<-c("SW", "FW")
+
+sodium_PCHANGE_CL_SUM$Time_Point_f = factor(sodium_PCHANGE_CL_SUM$Time_Point, levels=c("2", "3"))
+Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("2", "3")
+
+Sodium_PLOT_PCHANGE <- ggplot(sodium_PCHANGE_CL_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
+            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(21, 16,22, 15))+
+            theme_classic()+
+            ggtitle("Sodium")+
+            theme(plot.title = element_text(hjust = 0.5))+
+            theme(legend.position="", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Percentage Change \n",breaks = c(-10,0,10,20,30,40,50), limits = c(-10,50))+
+            scale_x_discrete(breaks=c("2", "3"),
+              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+
+
+            theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
+                  axis.text.x=element_text(size=16, colour="black"),
+                  axis.text.y=element_text(size=16, colour="black"))+
+                  theme(axis.text.x=element_text(size=16, angle = 0),
+                   axis.title.x=element_text(size=16),
+                   axis.title.y=element_text(size=18),
+                   strip.text.y=element_text(size=14,face="italic"),
+                   strip.text.x=element_text(size=16,face="italic"),
+                   legend.title = element_blank())+
+                   theme(legend.text=element_text(size=16))
+
+Sodium_PLOT_PCHANGE
+
+```
+
+##Potassium
+```{r}
+potassium_PCHANGE_CL_SUM$Session_f = factor(potassium_PCHANGE_CL_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+#Cl_SUM2$Speed_f = factor(Cl_SUM2$Speed, levels=c("SW", "FW"))
+ #Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ #names(Speed.labs)<-c("SW", "FW")
+
+potassium_PCHANGE_CL_SUM$Time_Point_f = factor(potassium_PCHANGE_CL_SUM$Time_Point, levels=c("2", "3"))
+Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("2", "3")
+
+potassium_PLOT_PCHANGE <- ggplot(potassium_PCHANGE_CL_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
+            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(21, 16,22, 15))+
+            theme_classic()+
+            ggtitle("Potassium")+
+            theme(plot.title = element_text(hjust = 0.5))+
+            theme(legend.position="", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Percentage Change \n",breaks = c(-10,0,10,20,30,40,50), limits = c(-10,50))+
+            scale_x_discrete(breaks=c("2", "3"),
+              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+
+
+            theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
+                  axis.text.x=element_text(size=16, colour="black"),
+                  axis.text.y=element_text(size=16, colour="black"))+
+                  theme(axis.text.x=element_text(size=16, angle = 0),
+                   axis.title.x=element_text(size=16),
+                   axis.title.y=element_text(size=18),
+                   strip.text.y=element_text(size=14,face="italic"),
+                   strip.text.x=element_text(size=16,face="italic"),
+                   legend.title = element_blank())+
+                   theme(legend.text=element_text(size=16))
+
+potassium_PLOT_PCHANGE
+
+```
+
+##Chloride
+```{r}
+chloride_PCHANGE_CL_SUM$Session_f = factor(chloride_PCHANGE_CL_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
+ Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
+ names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")
+
+#Cl_SUM2$Speed_f = factor(Cl_SUM2$Speed, levels=c("SW", "FW"))
+ #Speed.labs<- c("Low-Intensity","Moderate-Intensity")
+ #names(Speed.labs)<-c("SW", "FW")
+
+chloride_PCHANGE_CL_SUM$Time_Point_f = factor(chloride_PCHANGE_CL_SUM$Time_Point, levels=c("2", "3"))
+Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
+names(Time_Point.labs)<-c("2", "3")
+
+chloride_PLOT_PCHANGE <- ggplot(chloride_PCHANGE_CL_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
+            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
+            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+
+
+            scale_colour_manual(name = "Session_f",
+                            labels = Session_f.labs,
+                            values = c("black", "black", "black", "black"))+
+
+            scale_shape_manual(name = "Session_f",
+                           labels = Session_f.labs,
+                           values = c(21, 16,22, 15))+
+            theme_classic()+
+            ggtitle("Potassium")+
+            theme(plot.title = element_text(hjust = 0.5))+
+            theme(legend.position="", legend.title=element_blank())+
+            xlab("\n Collection Time Point")+
+            scale_y_continuous(name = "Percentage Change \n",breaks = c(-20,-10,0,10,20,30,40,50), limits = c(-20,50))+
+            scale_x_discrete(breaks=c("2", "3"),
+              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+
+
+            theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
+                  axis.text.x=element_text(size=16, colour="black"),
+                  axis.text.y=element_text(size=16, colour="black"))+
+                  theme(axis.text.x=element_text(size=16, angle = 0),
+                   axis.title.x=element_text(size=16),
+                   axis.title.y=element_text(size=18),
+                   strip.text.y=element_text(size=14,face="italic"),
+                   strip.text.x=element_text(size=16,face="italic"),
+                   legend.title = element_blank())+
+                   theme(legend.text=element_text(size=16))
+
+chloride_PLOT_PCHANGE
+
+```
+
 ```{r}
@@
 
-##Electrolyte Grouping
+#Electrolyte Grouping
 ```{r}
